---
title: "Analisi bayesiana di dati sperimentali" (appunti per un corso)
output: html_notebook
---

##Esperimento
In questo esperimento X topi sono stati randomizzati a 3 gruppi di trattamento e un gruppo di controllo. Per ogni singolo topo giornalmente, per 17 giorni,  è stato misurato il peso in grammi. L'ipotesi di lavoro è che i topi trattati avranno un -aumento di peso più rilevante rispetto a quello dei topi di controllo.

```{r include=FALSE}
source("librerie.r")
#df <- read.csv("D:/Dati/vito.tranquillo/gitProject/corsoBayes/datisp132.csv", sep=";")
df <- read.csv("datisp132.csv", sep=";")
```

```{r echo=FALSE}
head(df)
```

```{r echo=FALSE, warning=FALSE}
              
p <- ggplot(data = df, aes(x = giorno, y = peso, group = id, colour=id))
p+geom_point()
p+geom_line()+stat_smooth(aes(group = 1)) + stat_summary(aes(group = 1),geom = "point", fun.y = mean, shape = 17, size = 3)+ facet_grid(. ~ gruppo)+geom_point()
```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
